% Author: Cristian Gonzales
% Sprint 1 Report
%%%%%%%%%%%%%%%%%%%%

\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage[document]{ragged2e}

\newcommand\tab[1][1cm]{\hspace*{#1}}

\begin{document}
	\Large{\textbf{Sprint 1 Report}}\\
	\Large{\textbf{Product: Amazon Discount Finder}}\\
	\Large{\textbf{Team: Toonsquad}}\\
	\Large{\textbf{Date: October 23, 2017}}\\
	
	\vspace{-3mm}
	
	\section{Actions to stop doing}
		\vspace{-3mm}
		\tab \normalsize{Based off our last sprint, we believe that we should stay committed to keeping sprint meetings on Wednesday and Friday over Skype or Google Hangouts. Either forum will suffice. We are not in close proximity of each other, so at the current time, this is most convenient.}
		
	\section{Actions to start doing}
		\vspace{-3mm}
		\tab \normalsize{Actions that we should partake in is better communication on forums such as Slack and being more organized with Scrum documents. We believe that fixing this will keep our developers focused, punctual, and in the loop of the current status of our sprint (outside of sprint meetings, that is). Also, we should keep disciplined on the key things that are needed to be discussed during the sprint meeting.}
		
	\section{Actions to keep doing}
		\vspace{-3mm}
		\tab \normalsize{Things we should continue to do that will keep the dynamic of our group healthy is contributing and having a voice at Scrum meetings. Adding more functionality in early stages will make our project better.}
		
	\section{Work completed \& not completed}
		\vspace{-3mm}
		\normalsize{The following user stories from the sprint plan were completed:}\\
		\vspace{-3mm}
		\begin{itemize}
			\item As a developer, I want to decide what tools we will be working with and familiarize myself with them.
		\end{itemize}
		\vspace{-3mm}
		\normalsize{The uncompleted user stories are as follows:}\\
		\vspace{-3mm}
		\begin{itemize}		
			\item As a user, I want to be able to access items from Amazon.
		\end{itemize}
		\vspace{-3mm}
		
	\section{Work completion rate}
		\vspace{-3mm}
		\normalsize{Sprint 1}\\
		\vspace{-3mm}
		\begin{itemize}
			\item Total number of user stories completed during the sprint: 1
			\vspace{-3mm}
			\item Total number of estimated ideal work hours completed during the sprint: 20
			\vspace{-3mm}
			\item Total number of days during the sprint: 14
		\end{itemize}
	
\end{document}